\input{preamble.tex}

\begin{document}

\tableofcontents

\section{Optimal Combinations of Measurements}
\begin{itemize}

    \item Describe the relevance of the central limit theorem of the statistical distribution of noise.
    Describe noise arising from alternating-current power lines (Brumov šum) and derive its power spectrum $\dv{P}{} $

    \item Describe the properties and autocorrelation function of measurement noise (merilni šum) in both discrete and continuous time.

    \item Describe the scalar Kalman filter in both discrete and continuous time.

    \item Describe the vector Kalman filter in both discrete and continuous time.

    \item Describe the dynamic noise terms $\omega_{n}$ and $\Gamma$ used in our treatment of the Kalman filter.
    How do we explain dynamic noise in the limit $\Delta t \to 0$ (i.e. the transition from discrete to continuous time)?

\end{itemize}

\section{Sensors}
\begin{itemize}

    \item What is a sensor's transfer function and what is it used for?
    What are the transfer functions of first and second-order sensors?

    \item What are Bode plots and what are they used for?

    \item Derive the transfer function of a first-order sensor.

    \item Formulate a bicycle shock absorber as a second-order sensor and derive its transfer function.

    \item What is an instrumentation amplifier and what is it used for?
    What is a differnetial amplifier's common-mode rejection ratio?

    \item What are some of the important properties of thermal noise on a resistor?
    Describe the high-frequency limit of thermal noise's mean-squared voltage spectrum.
    
    \item Derive the mean-squared voltage spectrum of thermal noise on a resistor from the Bose-Einstein frequency distribution of the energy of ``standing waves'' in the resistor.

\end{itemize}

\section{Statistics}
\begin{itemize}

    \item Describe the chi-squared test for estimation of the population variance.

    \item Describe the Pearson chi-squared goodness-of-fit test and what it is used for.

    \item Describe the Kolmogorov goodness-of-fit test and what it is used for.

    \item Describe the method of least squares.
    How can this method be used to resolve spectral peaks?

\end{itemize}

\section{Practical Circuits}
\begin{itemize}

    \item Describe the basic working principles of a lock-in detector and some practical uses of lock-in detection.

    \item Describe the basic working principles of a phase-locked-loop (e.g. give its block-level diagram and describe each component) and some practical uses of phase-locked loops.
    Describe the importance of properly choose the regulatory filter's transfer function.

    \item Describe the working principles of a basic analog radio.

\end{itemize}

\section{Displacement Sensors}
\begin{itemize}

    \item Describe the physical principles and circuit of a capacitive displacement sensor.

    \item Describe the physical principles and circuit of a piezoelectric displacement sensor.

    \item Describe the physical principles and circuit of an inductive displacement sensor.

\end{itemize}

\end{document}

